Dirac integration with a general purpose bookkeeping DB: a complete general suite for distributed resources exploitation

### 2013-10-03 CHEP2013/paper/paper.tex
simulation production use case

\author{M Chrzaszcz, C De Santis, G Donvito, A Fella, R Grzymkowski, B Santeramo, L Tommassetti, M Zdybal}
%\address{\textsuperscript {1} Institution, Country}
\ead{bruno.santeramo@ba.infn.it}

@@

\section{Job wrapper component}
% Bruno, Armando
- general workflow\\
- data management policy: stage-in and stage out strategies\\

\section{Simulation production use case: the SuperB experience}
% Bruno
- general description: workflow, Dirac portal design\\
- past experience: the webui project\\
-- Session definition interface --> DB dynamic build up\\

@@

\section{Functionality Test}
% Bruno
A functionality test was performed to demonstrate the capability of SuperBDIRAC to integrate the monitoring of a bookkeeping database in DIRAC webportal.
\subsection{Goal description}
DIRAC capabilities and performance as job management tool are well documented (insert some reference). Super$B$ distributed simulation stack (WebUI + SBK + Severus) was successfully used in 3 simulation campaigns (ask to Armando for confirmation and references).\\
Functionality Test goal is to demonstrate if SuperBDIRAC is capable of substitute WebUI as monitoring tool for job submission, showing data from a bookkeeping database. Test "Q-factor" is the exact correspondence of information as stored in SBK and displayed in SuperBDIRAC, like in WebUI monitoring page. Correct execution of simulation jobs is not important while the bookkeping information are properly managed.

@@

%% \bibitem{ref:ganga}
%% \verb"http://ganga.web.cern.ch/ganga"

>>>>

\author{M Chrzaszcz, C De Santis$^1$, G Donvito$^2$, A Fella$^3$, R Grzymkowski, B Santeramo$^{2,4}$, L Tomassetti$^{5,6}$, M Zdybal}
%\address{\textsuperscript {1} Institution, Country}
\address{$^1$ INFN - Sezione di Roma Tor Vergata, Roma, Italy}
\address{$^2$ INFN - Sezione di Bari, Bari, Italy}
\address{$^3$ NFN - Sezione di Pisa, Pisa, Italy}
\address{$^4$ Dipartimento di Fisica dell’Universit\'a e del Politecnico di Bari, Bari, Italy}
\address{$^5$ Dipartimento di Matematica e Informatica, Universit\'a di Ferrara, Ferrara, Italy}
\address{$^6$ INFN - Sezione di Ferrara, Ferrara, Italy}
\ead{bruno.santeramo@ba.infn.it}

@@

\section{Job wrapper component}
\label{sec:severus}
% Bruno, Armando
- general workflow\\
- data management policy: stage-in and stage out strategies\\

\section{Simulation production use case: the SuperB experience}
% Bruno
Simulation Production is designed to manage huge MonteCarlo productions.
A webportal, named WebUI\cite{ref:webui}, is available to manage the entire stack of operations related to this use case: user management, definition of new "Sessions", "Productions" and "Request", job submission and monitoring, sites management for productions. 
Production manager users can add and delete sites, add and delete CEs and SEs, set a site a site as enabled/disabled and supported/unsopported for a given session, manage "Sessions", "Productions" and "Request". These actions involve only BookKeeping database, building up automatically required tables.
Shifter users can submit and monitor jobs for a given Request. Job submission in WebUI is performed via Ganga\cite{ref:ganga}, while configurations files for submission are generated by WebUI itself taking data from SBK. Ganga submit jobs to grid via WMS using standard gLite commands. Job execution on WNs is driven by Severus (see section \ref{sec:severus}), while job status updates in SBK is performed via REST interface. Stagein and Stageout as well as LFC registration of output files is performed even by Severus. See figure \ref{fig:simulation_production_workflow} for Simulation Production workflow.\\

SuperBDIRAC goal is porting WebUI functionalities in DIRAC to manage jobs, distributed resources and metadata related to a MonteCarlo production using a BookKeeping database.
Job submission is directly managed by DIRAC. Grid computing resources can be used via WMS or direct submission to CREAM CEs, computer clusters can be accessed via ssh connections, Cloud resources are available via VMDIRAC module, even desktop computers can be used via Boinc. User authentication via X509 certificates and authorization VOMS-role based are builtin in DIRAC.
SuperBDIRAC enhance DIRAC integrating the generic bookkeeping database SBK via SQLAlchemy.
DIRAC webportal is extended in order to provide an interface for Production manager actions as well as shifter tasks.
At present time not all WebUI functionalities are yet ported in SuperBDIRAC, but site and job monitoring from SBK are available.
In section \ref{sec:test} are reported results of first SuperBDIRAC functionality test.

%- general description: workflow, Dirac portal design\\
%- past experience: the webui project\\
%-- Session definition interface --> DB dynamic build up\\

@@

\section{Functionality Test}
\label{sec:test}
% Bruno
A functionality test was performed to demonstrate the capability of SuperBDIRAC to integrate the monitoring of a bookkeeping database in DIRAC webportal.
\subsection{Goal description}
DIRAC capabilities and performance as job management tool are well documented (insert some reference). Super$B$ distributed simulation stack (WebUI + SBK + Severus) was successfully used in 3 simulation campaigns (ask to Armando for confirmation and references).\\
Functionality Test goal is to demonstrate if SuperBDIRAC is capable of substitute WebUI as monitoring tool for job submission, showing data from a bookkeeping database. Test "Q-factor" is the exact correspondence of information as stored in SBK and displayed in SuperBDIRAC, like in WebUI monitoring page. Correct execution of simulation jobs is not important while the bookkeping information are properly managed.

@@

\bibitem{ref:ganga}
\verb"http://ganga.web.cern.ch/ganga"
